Community-Conditioned Language Models

### 2020-11-17 paper/paper.tex
quantify left out sub comment lengths

Our dataset includes messages from \num{46} subreddits, 
randomly selected from the set of all forums 
with at least \num{15000} messages per month for each month
in the three years between 2015 and 2017. 
We initially selected \num{50} subreddits, 
but excluded four of them from further analysis: 
two because they were primarily non-English and two with particularly\jp{quantify?} short average message lengths.
Each community corpus consist of \num{50000} randomly selected messages from the year 2015.

>>>>

Our dataset includes messages from \num{46} subreddits, 
randomly selected from the set of all forums 
with at least \num{15000} messages per month for each month
in the three years between 2015 and 2017. 
We initially selected \num{50} subreddits, 
but excluded four of them from further analysis: 
two because they were primarily non-English and two with particularly short average message lengths.\footnote{
The macro-average message length was \num{39.3} ($\sigma=15.7$) and the two removed communities had average comment lengths of \num{10.7} and \num{18.1}.}
Each community corpus consist of \num{50000} randomly selected messages from the year 2015.
